Chasing \rainbows \hspace{1pt} with the Habitable Worlds Observatory

### 2023-02-24 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/madness.pdf}  
    \caption{
        Eccentric orbits for the stellar sample $\IWA$ of 1, 2, 3 and 4~$\lambda / D$ corresponding to 21, 42, 63 and 84 mas.
        The habitable zone is identified in each panel. 
    }
    \label{fig:ball-o-yarn}
\end{figure*}

@@

full version cumulative distribution \\
- discussion of differences \\

>>>>

\textbf{Is there a plot for this?}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/madness.pdf}  
    \caption{
        A example of the eccentric orbits generated for the stellar sample. The orbits are scaled by the Earth-equivalent flux distance. The shaded region indicates \IWA's of 1, 2, 3 and 4~$\lambda / D$ corresponding to 21, 42, 63 and 84 mas. The \IWA can significantly affect the range of scattering phases observable with each orbit.
    }
    \label{fig:ball-o-yarn}
\end{figure*}

@@
